A comparison of design-based and model-based approaches for finite population spatial data.

### 2021-10-12 inst/manuscript/manuscript.Rmd
section 2 updates

---
title: A comparison of design-based and model-based approaches for spatial data.
author:
  - name: In alphabetical order Michael Dumelle
    email: Dumelle.Michael@epa.gov
    affiliation: USEPA
    footnote: 1
  - name: Matt Higham
    email: mhigham@stlaw.edu
    affiliation: STLAW
    footnote: 1
  - name: Lisa Madsen
    affiliation: OSU
  - name: Anthony R. Olsen
    affiliation: USEPA
  - name: Jay M. Ver Hoef
    affiliation: NOAA
address:
  - code: USEPA
    address: United States Environmental Protection Agency, 200 SW 35th St, Corvallis, Oregon, 97333
  - code: STLAW
    address: Saint Lawrence University Department of Mathematics, Computer Science, and Statistics, 23 Romoda Drive, Canton, New York, 13617
  - code: OSU
    address: Oregon State University Department of Statistics, 239 Weniger Hall, Corvallis, Oregon, 97331
  - code: NOAA
    address: Marine Mammal Laboratory, Alaska Fisheries Science Center, National Oceanic and Atmospheric Administration, Seattle, Washington, 98115
footnote:
  - code: 1
    text: "Corresponding Author"
abstract: |
  This is the abstract.

@@

<!-- Paragraph about the contribution of the manuscript and outlining the rest -->
Though comparisons between design-based and model-based approaches to spatial data have been studied, no numerical comparison has been made between design-based approaches that incorporate spatial locations and model-based approaches. In this manuscript, we compare design-based approaches that incorporate spatial locations to model-based approaches for spatial data. The rest of the manuscript is organized as follows. In Section \ref{sec:background}, we compare sampling and estimation procedures between the design-based approach and the model-based approach for spatial data. In Section \ref{sec:numstudy}, we use a simulation approach to study the behavior and performance of both approaches. In Section \ref{application}, we use both approaches to analyze real data. And in Section \ref{sec:discussion}, we end with a discussion and provide directions for future research.

@@

## Comparing Design-Based and Model-Based Approaches

The design-based approach assumes the population is fixed. Randomness is incorporated via the selection of units in a sampling frame according to a sampling design. A sampling frame is the set of all units available to be sampled. A sampling design assigns a positive probability of inclusion (inclusion probability) to each unit in the sampling frame. Some examples of commonly used sampling designs include simple random sampling, stratified random sample, and cluster
sampling. These sampling designs tend to select units from the sampling frame independently of other units, so we call them "Independent Random Sampling" (IRS) designs. The design-based approach combines the randomness of the sampling design and the data collected via the sample to estimate parameters (e.g. means and totals) of a population. Generally, these population parameters are assumed to be fixed, unknown constants.

@@

The model-based approach assumes the data are a random realization of a data-generating process. Randomness is often incorporated through distributional assumptions on this process and need not be incorporated through random sampling (bottom row of Figure \ref{fig:fig1}). Instead of estimating fixed but unknown parameters (as in the design-based approach), the goal of model-based inference in the spatial context is often to predict a realized variable, or value. For example, suppose the realized mean of all population units is the value of interest. Instead of \emph{estimating} a fixed, unknown mean, we are \emph{predicting} the value of the mean, a random variable. Prediction intervals are then derived leveraging assumptions of the data generating process. If we repeatedly generate the response values from a fixed spatial process and obtained a sample, then 95% of all 95% prediction intervals constructed from a procedure with appropriate coverage will contain their respective realized means. @cressie1993statistics and @schabenberger2017statistical provide reviews of model-based approaches for spatial data. A visual comparison of the design-based and model-based assumptinos is provided in Figure \ref{fig:fig1} (@brus2020statistical provides a similar figure).

@@

__Tony O.__: Before this section is it useful to have a section that lays out the general site selection and general analysis options. Thinking about site selection as design-based IRS, design-based GRTS, Arbitrary set of sites, selection for model-based. Then general analysis options as design-based no spatial, design-based spatial, model-based. This four by three table would show that model-based analyses are possible for all selection options. Design-based options with no spatial info possible for IRS-based and GRTS-based. Design-based options with spatial info possible for GRTS-based.

__Jay VH__: What about the design for model-based inference? Strictly speaking, it is fixed – there is no probabilistic use of a randomized design. However, we are going to have to deal with Diggle et al. (2010).

## Spatially Balanced Design and Analysis

__Lisa M.__: Need a more precise definition of "miniature" in this context, and need an example.

__Jay VH__: Saying "the distribution of the sampled population units mirrors the density of..." is confusing to me. Are these formal statistical definitions of distribution (cumulative distribution function) and density (probability density function)? Wouldn’t IRS sample be a miniature, as it should, on average, mirror a population?

The design-based approach can use spatial locations to obtain spatially balanced samples. First we discuss spatial balance with respect to the population [@stevens2004spatially]. A sample is spatially balanced with respect to the population if the sampled population units are a miniature of the population units. A sample is a miniature of the population if the distribution of the sampled population units mirrors the density of all population units. Spatial balance with respect to the population is different than spatial balance with respect to geography. A sample that is spatially balanced with respect to geography is spread out in some type of equidistant manner over geographical space and is not meant to be miniatures of the population. When we refer to spatial balance henceforth, we mean spatial balance with respect to the population.

Spatially balanced samples are useful because they tend to yield estimates that have lower variance than estimates constructed from sampling designs lacking spatial balance [@stevens2004spatially; @barabesi2011sampling; @grafstrom2013well; @robertson2013bas; @wang2013design; @benedetti2017spatiallyreview]. To quantify spatial balance, @stevens2004spatially proposed loss functions based on Voroni polygons. The first spatially balanced sampling algorithm that saw widespread use was the Generalized Random Tessellation Stratified [@stevens2004spatially]. Since GRTS was developed, several other spatially balanced sampling algorithms have emerged, including the Local Pivotal Method [@grafstrom2012spatially; @grafstrom2018spatially], Spatially Correlated Poisson Sampling [@grafstrom2012spatiallypoisson], Balanced Acceptance Sampling [@robertson2013bas], Within-Sample-Distance [@benedetti2017spatially], and Halton Iterative Partitioning [@robertson2018halton]. We focus on the Generalized Random Tessellation Stratified (GRTS) algorithm to select spatially balanced sampling because it has several attractive properties, including __Lisa M.__: List major attractive properties, and detailed by @stevens2004spatially and @dumelle2021spsurvey.

<!-- algorithms. -->

The GRTS algorithm is used to sample from finite and infinite populations and works by utilizing a mapping between two-dimensional and one-dimensional space. The population units in two-dimensional space are divided into cells using a hierarchical index. Population units are then mapped to a one-dimensional line via the hierarchical indexing. The line length of each population unit equals its inclusion probability. A systematic sample is conducted on the line and these samples are linked to a population unit in two-dimensional space, which results in the desired sample. @stevens2004spatially and @dumelle2021spsurvey provide further details.

@@

After collecting a sample using the GRTS algorithm, the data are used to estimate population parameters. The Horvitz-Thompson estimator [@horvitz1952generalization] yields unbiased estimates of population means and totals. For example, if $\tau$ is a population total, then the Horvitz-Thompson estimator of $\tau$ (denoted by $\hat{\tau}_{ht}$), is given by
\begin{align}\label{eq:ht}
  \hat{\tau}_{ht} = \sum_{i = 1}^n Z_i \pi_i^{-1},
\end{align}
where $Z_i$ and $\pi_i$ are the observed value and inclusion probability of the $i$th population unit selected in the sample. A similar formula exists for estimating the mean, $\mu$. @horvitz1952generalization and @sen1953estimate provide variance estimators for $\hat{\tau}_{ht}$, but they have two drawbacks. First, they rely on calculating $\pi_{ij}$, the probability that population unit $i$ and population unit $j$ are included in the sample, and this can be very difficult to calculate. Second, they ignore the spatial locations of the population units. To address these drawbacks, @stevens2003variance proposed a local neighborhood variance estimator. The local neighborhood variance estimator does not rely on $\pi_{ij}$, and it incorporates spatial locations by assigning higher weights to nearby observations. @stevens2003variance show this variance estimators tends to reduce the estimated standard error of $\hat{\tau}$, yielding narrower confidence confidence intervals for $\tau$.

@@

Finite Population Block Kriging (FPBK) is a model-based approach that expands the geostatistical Kriging framework to the finite population setting [@verhoef2008spatial]. Instead of basing inference off of a specific sampling design, we assume the data are generated by a spatial process. @verhoef2008spatial gives details on the theory of FPBK, but some of the basic principles are summarized below. Let $\mathbf{z} \equiv \{\text{z}(s_1), \text{z}(s_2), . . . , \text{z}(s_N) \}$ be a response vector at locations $s_1$, $s_2$, . . . , $s_N$ that can be measured at the $N$ population units and is represented as an $N \times 1$ vector. Suppose we want to predict some linear function of the response variable, $f(\mathbf{z}) = \mathbf{b}^\prime \mathbf{z}$, where $\mathbf{b}^\prime$ is a $1 \times N$ vector of weights. For example, if we want to predict the population total across all population units, then we would use a vector of 1's for the weights.

@@

However, we often only have a sample of the $N$ population units. Denoting quantities that are part of the sampled population units with a subscript \emph{s} and quantities that are part of the unsampled population units with a subscript \emph{u},

@@

We also assume that there is spatial correlation in $\bm{\delta}$, which can be modeled using a covariance function. It is common to assume the covariance function is second-order stationary and isotropic [@cressie1993statistics], and that the spatial covariance decreases as the separation between population units increases. Many spatial covariance functions exist, but the primary function we use throughout the simulations and applications in this manuscript is the exponential covariance function: the $i,j^{th}$ entry for $\cov(\bm{\delta})$ is
\mbox{}
\begin{align}\label{equation:expcov}
\cov(\delta_i, \delta_j) = \theta_1\exp(-3h_{i,j}/\theta_2) + \theta_3\mathbbm{1}\{\mathbf{h}_{i,j} = 0\}, 
\end{align}
where $h_{i,j}$ is the distance between population units $i$ and $j$, and $\bm{\theta}$ is a vector of spatial covariance parameters of the partial sill $\theta_1$, the range $\theta_2$, and the nugget $\theta_3$; and, $\mathbbm{1}$ is equal to 1 when distance $h_i,j$ is equal to 0, and equal to 0 otherwise. However, any spatial covariance function could be used in the place of the exponential, including functions that allow for non-stationarity or anisotropy [@chiles1999geostatistics, pp. 80-93].

__Lisa M.__ : Include formulas. Perhaps, but, these are very heavy in notation and matrix algebra. We might consider, however, adding the formulas to an Appendix.

With the above model formulation, the Best Linear Unbiased Predictor (BLUP) for $f(\mathbf{b}'\mathbf{z})$ and its prediction variance can be computed. While details of the derivation are in [@verhoef2008spatial], we note here that the predictor and its variance are both moment-based.

We note that we only use FPBK in this paper in order to focus more on comparing the design-based and model-based approaches. However, k-nearest-neighbors [@fix1951discriminatory; @ver2013comparison], random forest [@breiman2001random], Bayesian models [@chan2020bayesian], among others, can also be used to obtain predictions for a mean or total from spatially correlated responses in a finite population setting. We choose to use FPBK because it is faster than a Bayesian approach and random forest and because @ver2013comparison showed that the method outperforms k-nearest-neighbors in many scenarios.

@@

```{r, echo = FALSE}
tab <- matrix(c("IRS-Design", "IRS-Model", "GRTS-Design", "GRTS-Model"),
       nrow = 2) %>%
  as.table()
row.names(tab) <- c("Design", "Model")
library(knitr)
kable(tab, col.names = c("IRS", "GRTS"), caption = "\\label{tab:designanalysis} Types of Sampling Design and Analysis combinations considered in the simulation study. The columns give the two types of sampling designs while the rows give the two types of analyses.")
## I really want "Analysis" to appear as a row header and "Sampling Design" 
## to appear as a column header, but this isn't easy to figure out.
## I couldn't figure this out with xtable either so it might need to be
## made "by hand."
```

@@

```{r}
n <- c("50", "100", "200")
site_locations <- c("Random", "Gridded", "")
psill_ratio <- c("0", "0.5", "0.9")
resp_type <- c("Normal", "Lognormal", "")
parm_tab <- rbind(n, site_locations, psill_ratio, resp_type)
row.names(parm_tab) <- c("Sample Size (n)", "Site Locations", 
                         "Partial Sill / Total Variance", "Response Type")
kable(parm_tab, col.names = c("", "", ""),
      caption = "\\label{tab:parmtab} Simulation parameters. Total variability for all scenarios was 2 so that the partial sill was 0, 1, or 1.8.")
```

>>>>

---
title: A comparison of design-based and model-based approaches for finite population spatial data.
author:
  - name: Michael Dumelle
    email: Dumelle.Michael@epa.gov
    affiliation: USEPA
    footnote: 1
  - name: Matt Higham
    email: mhigham@stlaw.edu
    affiliation: STLAW
  - name: Lisa Madsen
    affiliation: OSU
  - name: Anthony R. Olsen
    affiliation: USEPA
  - name: Jay M. Ver Hoef
    affiliation: NOAA
address:
  - code: USEPA
    address: United States Environmental Protection Agency, 200 SW 35th St, Corvallis, Oregon, 97333
  - code: STLAW
    address: Saint Lawrence University Department of Mathematics, Computer Science, and Statistics, 23 Romoda Drive, Canton, New York, 13617
  - code: OSU
    address: Oregon State University Department of Statistics, 239 Weniger Hall, Corvallis, Oregon, 97331
  - code: NOAA
    address: Marine Mammal Laboratory, Alaska Fisheries Science Center, National Oceanic and Atmospheric Administration, Seattle, Washington, 98115
footnote:
  - code: 1
    text: "Corresponding Author"
abstract: |
  This is the abstract.

@@

<!-- Paragraph about the contribution of the manuscript and outlining the rest -->
Though comparisons between design-based and model-based approaches to spatial data have been studied, no numerical comparison has been made between design-based approaches that incorporate spatial locations and model-based approaches. In this manuscript, we compare design-based approaches that incorporate spatial locations to model-based approaches for spatial data. Though these comparisons generalize to both finite populations (e.g. point resources) and infinite populations (e.g. linear and areal resources), we focus on applications to finite populations. The rest of the manuscript is organized as follows. In Section \ref{sec:background}, we compare sampling and estimation procedures between the design-based approach and the model-based approach for spatial data. In Section \ref{sec:numstudy}, we use a simulation approach to study the behavior and performance of both approaches. In Section \ref{application}, we use both approaches to analyze real data. And in Section \ref{sec:discussion}, we end with a discussion and provide directions for future research.

@@

## Comparing Design-Based and Model-Based Approaches {#subsec:dvm_compare}

The design-based approach assumes the population is fixed. Randomness is incorporated via the selection of units in a sampling frame according to a sampling design. A sampling frame is the set of all units available to be sampled. A sampling design assigns a positive probability of inclusion (inclusion probability) to each unit in the sampling frame. Some examples of commonly used sampling designs include simple random sampling, stratified random sample, and cluster sampling. These sampling designs tend to select units from the sampling frame independently of other units, so we call them "Independent Random Sampling" (IRS) designs. Sampling designs incorporating the spatial locations of units in the sample frame are called spatially balanced designs. Spatially balanced designs can be obtained using the Generalized Random Tessellation Stratified (GRTS) algorithm [@stevens2004spatially], which we discuss in more detail in Section \ref{subsec:spb_design}. The design-based approach combines the randomness of the sampling design and the data collected via the sample to estimate parameters (e.g. means and totals) of a population. Generally, these population parameters are assumed to be fixed, unknown constants.

@@

The model-based approach assumes the data are a random realization of a data-generating process. Randomness is incorporated through distributional assumptions on this process. Strictly speaking, randomness need not be incorporated through random sampling, though @diggle2010geostatistical warn against preferential sampling Preferential sampling occurs when the process generating the data locations and the process being modeled are not independent of one another. To guard against preferential sampling, model-based approaches often still implement random sampling.

Instead of estimating fixed but unknown parameters (as in the design-based approach), the goal of model-based inference in the spatial context is often to predict a realized variable, or value. For example, suppose the realized mean of all population units is the value of interest. Instead of \emph{estimating} a fixed, unknown mean, we are \emph{predicting} the value of the mean, a random variable. Prediction intervals are then derived leveraging assumptions of the data generating process. If we repeatedly generate the response values from a fixed spatial process and obtained a sample, then 95% of all 95% prediction intervals constructed from a procedure with appropriate coverage will contain their respective realized means. @cressie1993statistics and @schabenberger2017statistical provide reviews of model-based approaches for spatial data. A visual comparison of the design-based and model-based assumptions is provided in Figure \ref{fig:fig1} (@brus2020statistical provides a similar figure).

@@

## Spatially Balanced Design and Analysis {#subsec:spb_design}

Spatially balanced samples can be obtained using the design-based approach. Spatially balanced samples are useful because parameter estimates from these samples tend to vary less than parameter estimates from samples that are not spatially balanced [@stevens2004spatially; @barabesi2011sampling; @grafstrom2013well; @robertson2013bas; @wang2013design; @benedetti2017spatiallyreview]. The first spatially balanced sampling algorithm that saw widespread use was the Generalized Random Tessellation Stratified (GRTS) algorithm [@stevens2004spatially]. To quantify the spatial balance of a sample, @stevens2004spatially proposed loss metrics based on Voroni polygons. Since GRTS was developed, several other spatially balanced sampling algorithms have emerged, including the Local Pivotal Method [@grafstrom2012spatially; @grafstrom2018spatially], Spatially Correlated Poisson Sampling [@grafstrom2012spatiallypoisson], Balanced Acceptance Sampling [@robertson2013bas], Within-Sample-Distance Sampling [@benedetti2017spatially], and Halton Iterative Partitioning Sampling [@robertson2018halton]. In this manuscript, we use Generalized Random Tessellation Stratified (GRTS) sampling because it has several attractive properties: GRTS sampling accommodates finite and infinite sampling frames; accommodates equal, unequal, and proportional (to) size inclusion probabilities; accommodates legacy (historical) sampling; accommodates a minimum distance between units in a sample; accommodates reverse hierarchically ordered replacement units in a sample (replacement units are units available to be sampled if an original unit cannot be sampled); and is available in the spsurvey R package @dumelle2021spsurvey.

The GRTS algorithm samples from finite and infinite populations by utilizing a mapping between two-dimensional and one-dimensional space. The units in the two-dimensional sampling frame are divided into cells using a hierarchical address. This hierarchical address is then used to map the units from two-dimensional space to a one-dimensional line where each unit's line length equals its inclusion probability. A systematic sample is conducted on the line and linked back to a unit in two-dimensional space, which results in the desired sample. @stevens2004spatially and @dumelle2021spsurvey provide further details.

@@

After selecting a GRTS sample, data are collected and used to estimate population parameters. To unbiasedly estimate population means and totals from sample data, one can use the Horvitz-Thompson estimator [@horvitz1952generalization]. If $\tau$ is a population total, the Horvitz-Thompson estimate of $\tau$, denoted by $\hat{\tau}_{ht}$, is is given by
\begin{align}\label{eq:ht}
  \hat{\tau}_{ht} = \sum_{i = 1}^n Z_i \pi_i^{-1},
\end{align}
where $Z_i$ is the value of the $i$th unit in the sample and $\pi_i$ is the inclusion probability of the $i$th unit in the sample. An estimate of the population mean is obtained by dividing $\hat{\tau}_{ht}$ by the population size.

While the Horvitz-Thompson estimator is unbiased for population means and totals, it is also important to quantify the uncertainty in these estimates. @horvitz1952generalization and @sen1953estimate provide variance estimators for $\hat{\tau}_{ht}$, but they have two drawbacks. First, these estimators rely on calculating $\pi_{ij}$, the probability that unit $i$ and unit $j$ are both in the sample -- this quantity can be challenging if not impossible to calculate analytically. Second, these estimators ignore the spatial locations of the units in the sampling frame. To address these two drawbacks simultaneously, @stevens2003variance proposed the local neighborhood variance estimator. The local neighborhood variance estimator does not rely on $\pi_{ij}$ and incorporates spatial locations -- for technical details see @stevens2003variance. @stevens2003variance show the local neigborhood variance estimator tends reduce $\text{Var}(\hat{\tau})$ compared to variance estimators ignoring spatial locations, yielding narrower confidence intervals for $\tau$.

@@

Finite Population Block Kriging (FPBK) is a model-based approach that expands the geostatistical Kriging framework to the finite population setting [@verhoef2008spatial]. Instead of basing inference off of a specific sampling design, we assume the data are generated by a spatial process. @verhoef2008spatial gives details on the theory of FPBK, but some of the basic principles are summarized below. Let ${\mathbf{z} \equiv \{\text{z}(s_1), \text{z}(s_2), . . . , \text{z}(s_N) \}}$ be a response vector at locations $s_1$, $s_2$, . . . , $s_N$ that can be measured at the $N$ population units and is represented as an $N \times 1$ vector. Suppose we want to predict some linear function of the response variable, $f(\mathbf{z}) = \mathbf{b}^\prime \mathbf{z}$, where $\mathbf{b}^\prime$ is a $1 \times N$ vector of weights. For example, if we want to predict the population total across all population units, then we would use a vector of 1's for the weights.

@@

We often only have a sample of the $N$ population units. Denoting quantities that are part of the sampled population units with a subscript \emph{s} and quantities that are part of the unsampled population units with a subscript \emph{u},

@@

In addition to assuming the expectation of $\bm{\delta}$ equals $\mathbf{0}$, we also assume that there is spatial correlation in $\bm{\delta}$ that can be modeled using a covariance function. It is common to assume the covariance function is second-order stationary and isotropic [@cressie1993statistics], and that the spatial covariance decreases as the separation between population units increases. Many spatial covariance functions exist, but the primary function we use throughout the simulations and applications in this manuscript is the exponential covariance function: the $i,j$th entry for $\cov(\bm{\delta})$ is
\mbox{}
\begin{align}\label{equation:expcov}
\cov(\delta_i, \delta_j) = 
\begin{cases} 
\sigma^2_{ps}\exp(-h_{i,j}/\phi) & h_{i,j} > 0 \\
\sigma^2_{ps} + \sigma^2_n & h_{i,j} = 0
\end{cases}
,
\end{align}
where $\sigma^2_{ps}$ is the partial sill measuring coarse-scale (correlated) variability, $\sigma^2_{n}$ is the nugget measuring fine-scale (indepenent) variability, $\phi$ is the range parameter measuring the distance-decay rate of the covariance, and $h_{i,j}$ is the Euclidean distance between population units $i$ and $j$. Any spatial covariance function could be used in the place of the exponential, however, including functions that allow for non-stationarity or anisotropy [@chiles1999geostatistics, pp. 80-93].

With the above model formulation, the Best Linear Unbiased Predictor (BLUP) for $f(\mathbf{b}'\mathbf{z})$ and its prediction variance can be computed. While details of the derivation are in [@verhoef2008spatial], we note here that the predictor and its variance are both moment-based, meaning they don't rely on any distributional assumptions.

We note that we only use FPBK in this paper in order to focus more on comparing the design-based and model-based approaches. However, k-nearest-neighbors [@fix1951discriminatory; @ver2013comparison], random forest [@breiman2001random], Bayesian models [@chan2020bayesian], among others, can also be used to obtain predictions for a mean or total from spatially correlated responses of a finite population. We choose to use FPBK because it is faster than a Bayesian approach and random forest and because @ver2013comparison showed that the method outperforms k-nearest-neighbors in many scenarios.

@@

```{r, echo = FALSE, results = "asis"}
tab <- matrix(c("IRS-Design", "IRS-Model", "GRTS-Design", "GRTS-Model"),
       nrow = 2) %>%
  as.table()
row.names(tab) <- c("IRS", "GRTS")
xtab1 <- xtable(tab, col.names = c("Design", "Model"), caption = "\\label{tab:designanalysis} Types of Sampling Design and Analysis combinations considered in the simulation study. The rows give the two types of sampling designs while the columns give the two types of analyses.")
align(xtab1) <- "r|ll"
names(xtab1) <- c("IRS", "GRTS")
print(xtab1, comment = FALSE)
## I really want "Analysis" to appear as a row header and "Sampling Design" 
## to appear as a column header, but this isn't easy to figure out.
## I couldn't figure this out with xtable either so it might need to be
## made "by hand."
```

@@

```{r, echo = FALSE, results = "asis"}
n <- c("50", "100", "200")
site_locations <- c("Random", "Gridded", "")
psill_ratio <- c("0", "0.5", "0.9")
resp_type <- c("Normal", "Lognormal", "")
parm_tab <- rbind(n, site_locations, psill_ratio, resp_type)
parm_tab[c(2, 4), 3] <- "-"
row.names(parm_tab) <- c("Sample Size (n)", "Layout", 
                         "Proportion of Dependent Error", "Response Type")
# library(knitr) kable with htlm has trouble with page breaks -- kable with latex harder for me than xtable
# kable(parm_tab, col.names = c("", "", ""),
#       caption = "\\label{tab:parmtab} Simulation parameters. Total variability for all scenarios was 2 so that the partial sill was 0, 1, or 1.8.")
parm_xtab <- xtable(parm_tab, caption = "\\label{tab:parmtab} Simulation parameters. Total variability for all scenarios was 2 so that the partial sill was 0, 1, or 1.8.")
align(parm_xtab) <- "r|lll"
print(parm_xtab, include.colnames = FALSE, hline.after = c(0, nrow(parm_xtab)), comment = FALSE)
```
